---
title: "README"
output: github_document
---

[![license](https://img.shields.io/github/license/mashape/apistatus.svg)](https://choosealicense.com/licenses/mit/)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Turn your for loop into a purrr map function.

We start with cats, because why not.


```{r}
library(tibble)
cats <- 
    tribble(
    ~Name, ~Good,
    "Suzie", TRUE,
    "George", TRUE,
    "Fred", FALSE,
    "Donald", FALSE,
    "Tibbles", TRUE
)
```

We completely forgat we have ifelse statements.

Only good cats get premium quality super-awesome-food. Bad cats get normal food.

We don't want to type to much, we are data scientist, and lazy. So we create a 
function to do our work.

```{r}
good_kitty <-function(x){
    if(x){"Premium"} else{
            "Normal"
    }}
good_kitty(TRUE)
good_kitty(FALSE)
```


We start with a for loop to add information to the dataframe.
We want to do something on every row. We want to run the good_kitty function
on every row in the Good column.


```{r}
cats$Food <- NA
for(cat in 1:nrow(cats)){
    cats$Food[cat] <- good_kitty(cats$Good[cat])
}
cats
```



Now onto purrr

```{r}
library(purrr)
cats$Food <- NA

cats$Food <- purrr::map_chr(.x = cats$Good, .f = good_kitty)
cats
```


